Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package

### 2020-08-23 paper.rmd
work on examples

---
title             : "Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package"
shorttitle        : "tidyLPA"

@@

``` {r, curry-mac-mclust}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3)
```

@@

We can use Mplus simply by changing the package argument for
`estimate_profiles()`:

``` {r, curry-mac-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "MplusAutomation")
```

A simple summary of the analysis is printed to the console. 
The resulting object can be further passed down a pipeline to
other functions, such as `compare_solutions`, `get_data`, `get_fit`,
etc. This is the "tidy" part, in that the function can be embedded in a tidy
analysis pipeline.

If you have Mplus installed, you can call the version of this function that uses
MPlus in the same way, by adding the argument `package = "MplusAutomation`.

>>>>

---
title             : "Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package"
shorttitle        : "tidyLPA"

@@

We can see a number of statistics for each of the models that were estimated, including the 
AIC (Aikake information criterion; based on -2 log-likelihood, and penalized by number of parameters) and BIC (BIC: Bayesian information criterion; based on -2 log-likelihood, and penalized by number of parameters adjusted by sample size). Both are _penalized_ likelihood statistics; the log-likelihood will always decrease with the addition of additional 
paremeters estimated by the model, whereas the AIC and BIC will account for the number of parameters; lower values of
either indicate better fit.

Entropy. `prob_min` refers to the minimum of the diagonal of the average latent class probabilities for most likely class membership, by assigned class. The minimum should be as high as possible, reflecting greater classification certainty (cases are assigned to classes they have a high probability of belonging to; see Jung & Wickrama, 2008); `prob_max`
refers to the maximum. Finally. `n_min` refers to the proportion of the sample assigned to the smallest class (based on most likely class membership); `n_max` to the largest. Finally, `BLRT_p` refers to the p-value for the bootstrapped likelihood ratio test; a value greater than .05 indicates that the model fit better than one with one fewer class.

``` {r, curry-mac-mclust}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10)
```

Additional fit statistics (other penalized likelihood values, such as the CAIC, SABIC, and ICL), and the bootstrapped LRT 
test statistic, can be obtained with the `get_fit()` function:

```{r}
get_fit(m1)
```

@@

We can use Mplus simply by changing the package argument for
`estimate_profiles()` to "mplus" or "MplusAutomation" (either will work):

``` {r, curry-mac-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "mplus")
```

A simple summary of the analysis is printed to the console. 
The resulting object can be further passed down a pipeline to
other functions, such as `compare_solutions`, `get_data`, and `get_fit`.
